---
title: "Cabbages"
author: "Lelainy Saavedra!"
date: "September 11, 2020"
output:
  html_document:
    df_print: paged
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
require(MASS)
veggy <- cabbages
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->
 The cabbages data from the MASS package is loaded into a dataframe called veggy. Complete this report by answering the following two questions  
 
### Is there a difference in average VitC between c39 and c52 cultivation methods?  
```{r}
boxplot(VitC ~Cult,data=veggy)
```



# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

Response variable vitamin c is numerical, cultivation methods are categorical
# Results



<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->
```{r}
boxplot(VitC~ Cult,data=veggy)


```






```{r}

```

### Numerical Descriptive Results
The question is; Is there a difference in the vitamin C due to cultivation

$H_O$: There is no difference in the vitamin C due to cultivation
$H_A$:There is a difference in vitamin C due to cultivation

```{r}
 t.test(VitC~Cult,data=veggy)
```


<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->



## Inferential Results


It appears from the boxplot, tha cultivation method c52 results in higherVitamin C content




<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->


# Discussion and Conclusion


The P.value is 0.00000003 < 0.05 The null Hypothesis is extremely unlikely we reject the null hypothesis.
We conclude that there is a difference between the methods of cultivation and the vitamin C content.

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->
